---
title: "Play or Save the Theme from Star Wars"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Play or Save the Theme from Star Wars}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Create a vector for the notes of the Star Wars theme.  I like to do this by thinking about strings of notes for each bar of music and then using `strsplit()` to convert this to a vector with each note as an entry.  

``` {r eval = FALSE}
starwars_pitch <- paste(
  "D D D",
  "G D5",
  "C5 B A G5 D5",
  "C5 B A G5 D5",
  "C5 B C5 A D D D",
  "G D5",
  "C5 B A G5 D5",
  "C5 B A G5 D5",
  "C5 B C5 A D D",
  "E E C5 B A G",
  "G A B A E F# D D",
  "E E C5 B A G",
  "D5 A D D",
  "E E C5 B A G",
  "G A B A E F# D5 D5",
  "G5 F5 D#5 D5 C5 A# A G",
  "D5 D D D",
  "G D5",
  "C5 B A G5 D5",
  "C5 B A G5 D5",
  "C5 B C5 A D D D",
  "G D5",
  "C5 B A G5 D5",
  "G5 F5 D#5 Bb5 A5",
  "G5 G G G G"
)

starwars_pitch <- strsplit(starwars_pitch, " ")[[1]]
```

Now create a similar vector with the durations of each notes as proportion of a beat.  This vector should be the same length as the notes vector.  I like to do this with a line for each bar of music.

``` {r eval = FALSE}
starwars_duration <- c(
  0.33, 0.33, 0.33, 
  2, 2, 
  0.33, 0.33, 0.33, 2, 1, 
  0.33, 0.33, 0.33, 2, 1, 
  0.33, 0.33, 0.33, 2, 0.33, 0.33, 0.33, 
  2, 2, 
  0.33, 0.33, 0.33, 2, 1, 
  0.33, 0.33, 0.33, 2, 1, 
  0.33, 0.33, 0.33, 2, 0.75, 0.25,
  1.5, 0.5, 0.5, 0.5, 0.5, 0.5, 
  0.33, 0.33, 0.33, 0.75, 0.25, 1, 0.75, 0.25, 
  1.5, 0.5, 0.5, 0.5, 0.5, 0.5,
  1, 2, 0.75, 0.25,
  1.5, 0.5, 0.5, 0.5, 0.5, 0.5, 
  0.33, 0.33, 0.33, 0.75, 0.25, 1, 0.75, 0.25, 
  0.75, 0.25, 0.75, 0.25, 0.75, 0.25, 0.75, 0.25, 
  3, 0.33, 0.33, 0.33,   
  2, 2, 
  0.33, 0.33, 0.33, 2, 1, 
  0.33, 0.33, 0.33, 2, 1, 
  0.33, 0.33, 0.33, 2, 0.33, 0.33, 0.33, 
  2, 2, 
  0.33, 0.33, 0.33, 2, 1, 
  0.33, 0.33, 0.33, 2, 1, 
  1,  0.33, 0.33, 0.33, 1
)

```

To play or save, pick the right tempo and go:

``` {r eval = FALSE}

play_music(starwars_pitch, starwars_duration, tempo = 160)

save_music(starwars_pitch, starwars_duration, output_file = "starwars.wav", tempo = 160)

```
