---
title: "Play or Save Jingle Bells"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Play or Save Jingle Bells}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Create a vector for the notes of Jingle Bells.  I like to do this by thinking about strings of notes for each bar of music and then using `strsplit()` to convert this to a vector with each note as an entry.  Here I am writing quite a fun, virtuoso version of Jingle Bells.

``` {r eval = FALSE}
jbells_pitch <- paste(
  "E E E",
  "E E E",
  "E G C D",
  "E",
  "F F F F",
  "F E E E",
  "E D D E",
  "D G",
  "E E E",
  "E E E",
  "E G C D",
  "E",
  "F F F F",
  "F E E E E",
  "G G F D",
  "C",
  "G3 E D C",
  "G3",
  "G3 G3 G3 E D C",
  "A3",
  "A3 F E D",
  "B3",
  "G G F D",
  "E",
  "G3 E D C",
  "G3",
  "G3 E D C",
  "A3 A3", 
  "A3 F E D",
  "G G G G A G F D",
  "C C5 B A G F G",
  "E E E G C D",
  "E E E G C D",
  "E F G A C E D F",
  "E C D E F G A G",
  "F F F F F F",
  "F E E E E E",
  "E D D D D E",
  "D D E F G F E D",
  "E E E G C D",
  "E E E G C D",
  "E F G A C E D F",
  "E C D E F G A G",
  "F F F F F F",
  "F E E E E E",
  "G C5 B A G F E D",
  "C C E G C5"
)

jbells_pitch <- strsplit(jbells_pitch, " ")[[1]]

```

Now create a similar vector with the durations of each notes as proportion of a beat.  This vector should be the same length as the notes vector.  I like to do this with a line for each bar of music.

``` {r eval = FALSE}
jbells_duration <- c(
  1, 1, 2, 
  1, 1, 2, 
  1, 1, 1.5, 0.5, 
  4, 
  1, 1, 1, 1, 
  1, 1, 1, 1, 
  1, 1, 1, 1,
  2, 2,
  1, 1, 2, 
  1, 1, 2, 
  1, 1, 1.5, 0.5, 
  4, 
  1, 1, 1, 1, 
  1, 1, 1, 0.5, 0.5, 
  1, 1, 1, 1,
  4,
  1, 1, 1, 1, 
  3, .5, .5, 
  1, 1, 1, 1, 
  4,
  1, 1, 1, 1, 
  4,
  1, 1, 1, 1, 
  4,
  1, 1, 1, 1, 
  4,
  1, 1, 1, 1, 
  3, 1,
  1, 1, 1, 1,
  1, 1, 1, 1, 
  1, 1, 1, 1, 
  1, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5,
  1, 1, 0.5, 0.5, 0.5, 0.5, 
  1, 1, 0.5, 0.5, 0.5, 0.5,
  0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5,
  0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5,
  1, 0.5, 0.5, 1, 0.5, 0.5, 
  1, 0.5, 0.5, 1, 0.5, 0.5, 
  1, 0.5, 0.5, 0.5, 0.5, 1,
  1, 0.33, 0.33, 0.33, 1, 0.33, 0.33, 0.33,
  1, 1, 0.5, 0.5, 0.5, 0.5, 
  1, 1, 0.5, 0.5, 0.5, 0.5,
  0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5,
  0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5,
  1, 0.5, 0.5, 1, 0.5, 0.5, 
  1, 0.5, 0.5, 1, 0.5, 0.5, 
  0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5,
  1, 0.33, 0.33, 0.33, 2
)

```

To play or save, pick the right tempo and go:

``` {r eval = FALSE}

play_music(jbells_pitch, jbells_duration, tempo = 240)

save_music(jbells_pitch, jbells_duration, output_file = "jbells.wav", tempo = 240)

```
